---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%",
  cache = TRUE
)
```
# cookiemonster

The goal of cookiemonster is to add a festive picture of Cookie Monster above a  line-up protocol plot, in reference to [Graphical inference](https://www.youtube.com/watch?v=rEHKm3Z1zUE) by Hadley Wickham.  

This small package would not have been here without [Thomas Lin Pedersen's](https://twitter.com/thomasp85) [patchwork](https://github.com/thomasp85/patchwork). 
 
## Installation

You can install patchwork from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/cookiemonster")
```

## Examples

Due to the flexibility of `patchwork` we are able to have a quite relaxed notation.

```{r, eval=FALSE}
library(ggplot2)
library(nullabor)
library(patchwork)
library(cookiemonster)
cookiemonster(data = mtcars, var = "mpg") +
  aes(mpg, wt) +
  geom_point()

cookiemonster(mtcars, aes(mpg, wt), "mpg") +
  geom_point()
```

```{r echo=FALSE}
library(ggplot2)
library(nullabor)
library(patchwork)
library(cookiemonster)
cookiemonster(mtcars, var = "mpg") +
  aes(mpg, wt) +
  geom_point()
```

And we can check whether our guess is correct or not

```{r}
decrypt("WOXC 1IZI Tx t4nTZT4x p")
```

## More examples

```{r}
cookiemonster(mtcars, var = "cyl", procent = 0.2, n = 15, nrow = 3) +
  geom_boxplot(aes(cyl, mpg, group = cyl))
```

```{r}
cookiemonster(mtcars, aes(mpg, wt), "mpg") +
  geom_point() +
  theme_bw() +
  stat_smooth()
```
